---
title: "bootstrapping_methodComparison"
format:
  html: default
  pdf: default
editor: visual
execute:
  echo: true
  warning: true
  error: true
---

## Comparing the methods that I used to measure CTmin and CTmax in 2016-2017

and 2022:

Packages and working directory

```{r}
library(lme4)
library(cowplot)
library(boot)
library(ggplot2)
```

```{r}
setwd("C:/Users/jhanc/Box/PhD/Classes_per_year/Sixth year/Machine learning
      /Final_Project")

lizard_data <- read.csv("finalLizard_data.csv", header=TRUE) 
head(lizard_data)
```

Let's do a bootstrap for CTmin to check how the coefficients change for both methods, in this part we're going to use the raw data for CTmin

```{r}
# Define a function to calculate slope
slope_fn <- function(lizard_data, indices) {
  d <- lizard_data[indices, ]
  model <- lm(CTmin ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(lizard_data[lizard_data$Method == "M1", ], slope_fn, R = 10000)
boot_M2 <- boot(lizard_data[lizard_data$Method == "M2", ], slope_fn, R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)
```

Let's visualize the results from the bootstrap

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_ctmin <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmin_1 <- ggplot(boot_data_ctmin, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[min]~("째"*C))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 2400, 400), limit = c(0, 2400)) +
  scale_x_continuous(breaks = seq(-0.004, -0.0005, 0.001), limit = c(-0.004, 
                                                                     -0.0005)) +
  
    # theme(panel.background = element_rect(fill = NA, colour = NA), 
  #       plot.background = element_rect(fill = NA, colour = NA),
  #       legend.key = element_rect(fill = NA, colour = NA), 
  #       legend.background = element_rect(fill = NA, colour = NA),
  #       legend.text=element_text(family="serif", size=15),
  #       legend.title=element_blank(),
  #       legend.position = c(.85, .9),
  #       plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmin_1)
```

Let's do a bootstrap for CTmax to check how the coefficients change for both methods, in this part we're going to use the raw data for CTmAX

```{r}
# Define a function to calculate slope
slope_fn <- function(lizard_data, indices) {
  d <- lizard_data[indices, ]
  model <- lm(CTmax ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(lizard_data[lizard_data$Method == "M1", ], slope_fn, R = 10000)
boot_M2 <- boot(lizard_data[lizard_data$Method == "M2", ], slope_fn, R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)

```

Let's visualize the results from the bootstrap

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_ctmax <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmax_1 <- ggplot(boot_data_ctmax, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[max]~("째"*C))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 2650, 500), limit = c(0, 2650)) +
  scale_x_continuous(breaks = seq(-0.005, 0, 0.001), limit = c(-0.005, 0)) +
  
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmax_1)
```

Let's use the standarized data for CTmin and CTmax now

```{r}
data_M1 <- lizard_data[lizard_data$Method == "M1", ]
data_M2 <- lizard_data[lizard_data$Method == "M2", ]

# Standardize `x` and `y` within each year
data_M1$CTmin_std <- scale(data_M1$CTmin)
data_M1$CTmax_std <- scale(data_M1$CTmax)
data_M2$CTmin_std <- scale(data_M2$CTmin)
data_M2$CTmax_std <- scale(data_M2$CTmax)

# Combine back into a single dataset
data_std <- rbind(data_M1, data_M2)
# data_std
# write.csv(data_std, file = "Lizard_data_std_Nov10.csv")
```

Let's do a bootstrap for CTmin_std to check how the coefficients change for both methods, in this part we're going to use the raw data for CTmin_std

```{r}
# Define a function to calculate slope
slope_fn <- function(data_std, indices) {
  d <- data_std[indices, ]
  model <- lm(CTmin_std ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(data_std[data_std$Method == "M1", ], slope_fn, R = 10000)
boot_M2 <- boot(data_std[data_std$Method == "M2", ], slope_fn, R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)
```

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_CTmin_std <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmin_std_1 <- ggplot(boot_data_CTmin_std, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[min]~(std))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 6000, 1000), limit = c(0, 6000)) +
  scale_x_continuous(breaks = seq(-0.0015, 0, 0.0005), limit = c(-0.0015, 0)) +
  
  
  theme(panel.background = element_rect(fill = NA, colour = NA), 
        plot.background = element_rect(fill = NA, colour = NA),
        legend.key = element_rect(fill = NA, colour = NA), 
        legend.background = element_rect(fill = NA, colour = NA),
        legend.text=element_text(family="serif", size=20),
        legend.title=element_blank(),
        legend.position = c(.82, .90),
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  

  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmin_std_1)
```

Analysis for CTmax

```{r}
# Define a function to calculate slope
slope_fn <- function(data_std, indices) {
  d <- data_std[indices, ]
  model <- lm(CTmax_std ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(data_std[data_std$Method == "M1", ], slope_fn, R = 10000)
boot_M2 <- boot(data_std[data_std$Method == "M2", ], slope_fn, R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)
```

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_CTmax_std <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmax_std_1 <- ggplot(boot_data_CTmax_std, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[max]~(std))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 6000, 1000), limit = c(0, 6000)) +
  scale_x_continuous(breaks = seq(-0.0015, 0, 0.0005), limit = c(-0.0015, 
                                                                 -0.0004)) +
  
  # theme(panel.background = element_rect(fill = NA, colour = NA), 
  #       plot.background = element_rect(fill = NA, colour = NA),
  #       legend.key = element_rect(fill = NA, colour = NA), 
  #       legend.background = element_rect(fill = NA, colour = NA),
  #       legend.text=element_text(family="serif", size=15),
  #       legend.title=element_blank(),
  #       legend.position = c(.85, .9),
  #       plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmax_std_1)
```

```{r}
# png("Comparison_All_Nov09.png", height = 9, width = 14, units = "in", res = 300)
# plot_grid(ctmin_1, ctmax_1,  ctmin_std_1, ctmax_std_1,
#           labels = c("(a)", "(b)", "(c)", "(d)"),
#           ncol = 2, nrow = 2, label_fontfamily = "serif", label_size = 23,
#           label_y = 1.01, label_x = -0.02, label_fontface = "bold")
# 
# dev.off()

```

Let's run it now excluding the localities that are not share between years (e.g., Anchicaya, Tabio and La Sierpe)

```{r}
lizard_data_3pop <- read.csv("Lizard_data_3pop.csv", header=TRUE) 
head(lizard_data_3pop)
```

For CTmin

```{r}
# Define a function to calculate slope
slope_fn <- function(lizard_data_3pop, indices) {
  d <- lizard_data[indices, ]
  model <- lm(CTmin ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(lizard_data_3pop[lizard_data_3pop$Method == "M1", ], slope_fn, 
                R = 10000)
boot_M2 <- boot(lizard_data_3pop[lizard_data_3pop$Method == "M2", ], slope_fn, 
                R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)
```

Let's visualize the results from the bootstrap

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_CTmin_3pop <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmin <- ggplot(boot_data_CTmin_3pop, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[min]~("째"*C))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 2400, 400), limit = c(0, 2400)) +
  scale_x_continuous(breaks = seq(-0.003, -0.001, 0.0005), limit = c(-0.003, 
                                                                     -0.001)) +
  
  # theme(panel.background = element_rect(fill = NA, colour = NA), 
  #       plot.background = element_rect(fill = NA, colour = NA),
  #       legend.key = element_rect(fill = NA, colour = NA), 
  #       legend.background = element_rect(fill = NA, colour = NA),
  #       legend.text=element_text(family="serif", size=15),
  #       legend.title=element_blank(),
  #       legend.position = c(.85, .9),
  #       plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmin)
```

For CTmax

```{r}
# Define a function to calculate slope
slope_fn <- function(lizard_data_3pop, indices) {
  d <- lizard_data[indices, ]
  model <- lm(CTmax ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(lizard_data_3pop[lizard_data_3pop$Method == "M1", ], slope_fn, 
                R = 10000)
boot_M2 <- boot(lizard_data_3pop[lizard_data_3pop$Method == "M2", ], slope_fn, 
                R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)
```

Let's visualize the results from the bootstrap

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_CTmax_3pop <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmax <- ggplot(boot_data_CTmax_3pop, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[max]~("째"*C))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 2800, 400), limit = c(0, 2800)) +
  scale_x_continuous(breaks = seq(-0.002, -0.0005, 0.0005), limit = c(-0.002, 
                                                                      -0.0005)) +
  
  # theme(panel.background = element_rect(fill = NA, colour = NA), 
  #       plot.background = element_rect(fill = NA, colour = NA),
  #       legend.key = element_rect(fill = NA, colour = NA), 
  #       legend.background = element_rect(fill = NA, colour = NA),
  #       legend.text=element_text(family="serif", size=12),
  #       legend.title=element_blank(),
  #       legend.position = c(.85, .9),
  #       plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  # 
    theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmax)
```

Let's use the standarized data for CTmin and CTmax now

```{r}
data_M1 <- lizard_data_3pop[lizard_data_3pop$Method == "M1", ]
data_M2 <- lizard_data_3pop[lizard_data_3pop$Method == "M2", ]

# Standardize `x` and `y` within each year
data_M1$CTmin_std <- scale(data_M1$CTmin)
data_M1$CTmax_std <- scale(data_M1$CTmax)
data_M2$CTmin_std <- scale(data_M2$CTmin)
data_M2$CTmax_std <- scale(data_M2$CTmax)

# Combine back into a single dataset
data_std_3pop <- rbind(data_M1, data_M2)
# data_std_3pop
```

```{r}
# Define a function to calculate slope
slope_fn <- function(data_std_3pop, indices) {
  d <- data_std_3pop[indices, ]
  model <- lm(CTmin_std ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(data_std_3pop[data_std_3pop$Method == "M1", ], slope_fn, 
                R = 10000)
boot_M2 <- boot(data_std_3pop[data_std_3pop$Method == "M2", ], slope_fn, 
                R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)
```

Let's visualize the results from the bootstrap

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_CTmin_3pop_std <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmin_std <- ggplot(boot_data_CTmin_3pop_std, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[min]~(std))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 2800, 400), limit = c(0, 2800)) +
  scale_x_continuous(breaks = seq(-0.002, 0.001, 0.001), limit = c(-0.002, 
                                                                   0.001)) +
  
  # theme(panel.background = element_rect(fill = NA, colour = NA), 
  #       plot.background = element_rect(fill = NA, colour = NA),
  #       legend.key = element_rect(fill = NA, colour = NA), 
  #       legend.background = element_rect(fill = NA, colour = NA),
  #       legend.text=element_text(family="serif", size=15),
  #       legend.title=element_blank(),
  #       legend.position = c(.85, .9),
  #       plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmin_std)
```

For CTmax

```{r}
# Define a function to calculate slope
slope_fn <- function(data_std_3pop, indices) {
  d <- data_std_3pop[indices, ]
  model <- lm(CTmax_std ~ Elevation, data = d)
  return(coef(model)[2])  # Return the slope
}

# Bootstrapping for each year
set.seed(123)
boot_M1 <- boot(data_std_3pop[data_std_3pop$Method == "M1", ], slope_fn, 
                R = 10000)
boot_M2 <- boot(data_std_3pop[data_std_3pop$Method == "M2", ], slope_fn, 
                R = 10000)

boot_M1
boot_M2

# Calculate confidence intervals for boot_year1
ci_M1 <- boot.ci(boot_M1, type = "bca")
ci_M2 <- boot.ci(boot_M2, type = "bca")

# Print confidence intervals
print(ci_M1)
print(ci_M2)


# Compare bootstrap distributions
plot(boot_M1)
plot(boot_M2)
```

Let's visualize the results from the bootstrap

```{r}
# For visualization
# Combine bootstrap results into a data frame for plotting
boot_data_CTmax_3pop_std <- data.frame(
  slope = c(boot_M1$t, boot_M2$t),
  method = factor(rep(c("M1", "M2"), each = 10000)))

# Plotting the bootstrap distributions
ctmax_std <- ggplot(boot_data_CTmax_3pop_std, aes(x = slope, fill = method)) +
  geom_density(alpha = 0.7, color = "black", size = 1) +
  labs(x = "Slope") +
  
  ylab(expression(Density~CT[max]~(std))) +
  
  theme_classic() +
  scale_fill_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_color_manual(values=c("#EF8354", "#4F5D75"),
                     breaks = c("M1", "M2"),
                     labels = c(expression(bold("M1;")~"2016-2017"), 
                               expression(bold("M2;")~"2022"))) +
  
  scale_y_continuous(breaks = seq(0, 2600, 400), limit = c(0, 2600)) +
  scale_x_continuous(breaks = seq(-0.002, 0, 0.001), limit = c(-0.002, 0)) +
  
  # theme(panel.background = element_rect(fill = NA, colour = NA), 
  #       plot.background = element_rect(fill = NA, colour = NA),
  #       legend.key = element_rect(fill = NA, colour = NA), 
  #       legend.background = element_rect(fill = NA, colour = NA),
  #       legend.text=element_text(family="serif", size=15),
  #       legend.title=element_blank(),
  #       legend.position = c(.85, .9),
  #       plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  
  theme(axis.text.x = element_text(family="serif", size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.text.y = element_text(family="serif",size = 22, lineheight = 0.9, 
                                   vjust = 1)) +
  theme(axis.title.y = element_text(family="serif",vjust=1.2, size=30)) +
  theme(axis.title.x = element_text(family="serif",vjust=-0.5, size=30))

print(ctmax_std)
```

```{r}
# png("Comparison_3Pop_Nov09.png", height = 9, width = 14, units = "in", res = 300)
# plot_grid(ctmin, ctmax,  ctmin_std, ctmax_std,
#           labels = c("(a)", "(b)", "(c)","(d)"),
#           ncol = 2, nrow = 2, label_fontfamily = "serif", label_size = 23,
#           label_y = 1.01, label_x = -0.02, label_fontface = "bold")
# 
# dev.off()
```

```{r}
# png("Comparison_All_Nov27.png", height = 20, width = 14, units = "in", res = 300)
# plot_grid(ctmin_1, ctmin_std_1, ctmax_1,  ctmax_std_1,
#           ctmin, ctmin_std, ctmax,  ctmax_std,
#           labels = c("(a)", "(b)", "(c)", "(d)",
#                      "(e)", "(f)", "(g)","(h)"),
#           ncol = 2, nrow = 4, label_fontfamily = "serif", label_size = 23,
#           label_y = 1.01, label_x = -0.02, label_fontface = "bold")
# 
# dev.off()
```
